The five pillars of computational reproducibility: Bioinformatics and beyond

### 2023-06-12 manuscript/5pillars.Rmd
documentation edits
fix citation

The article should have clear links to supporting materials including datasets, software code and
other resources like computational environments.
The code repository should have a detailed `README` file which plays a critical role in reproducibility.
It should outline the purpose of the code/software/overall project and how it relates to the
article.
For example, some articles may rely on more than one repository for various parts of the research
project, so these need to be explained.

@@

The key technological advances enabling the five pillars approach have been around for about a decade,
yet progress on integrating these into computational research publications has been minimal.
Indeed the number of systematic replication studies in bioinformatics remains small
[@Zaringhalam2020-ms ; @Ioannidis2009-hv; @Samuel2022-ha], so the severity of the problem isn't
well understood.
Part of the problem is the incentive structures in academia, with funding bodies and journals
largely focused on novel research directions rather than confirming previous findings
[@Garijo2013-zl ; @Huang2013-xr; @Kaelin2017-id; @Munafo2017-ty; @Diong2021-is].

>>>>

The article should have clear links to supporting materials including datasets, software code and
other resources like computational environments.

The code repository should have a detailed `README` file which plays a critical role in reproducibility.
It should outline the purpose of the code/software/overall project and how it relates to the
article.
For example, some articles may rely on more than one repository for various parts of the research
project, so these need to be explained.

@@

The key technological advances enabling the five pillars approach have been around for about a decade,
yet progress on integrating these into computational research publications has been minimal.
Indeed the number of systematic replication studies in bioinformatics remains small
[@Ioannidis2009-hv; @Zaringhalam2020-ms; @Samuel2022-ha], so the severity of the problem isn't
well understood.
Part of the problem is the incentive structures in academia, with funding bodies and journals
largely focused on novel research directions rather than confirming previous findings
[@Garijo2013-zl ; @Huang2013-xr; @Kaelin2017-id; @Munafo2017-ty; @Diong2021-is].
